--- 
title: "Statistical Writing"
author: "Elizabeth Schifano and Jun Yan"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib, jyan.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a book developed using the bookdown package. The output format for this example is bookdown::gitbook."
---

# Preface {-}

This book aims to train students in statistics and data science on statistical
writing with professional tools such as LaTeX, BibTeX, R, and Git. It is based
on my writing experience of over 20 years and 100 scholarly papers. Many of the
tips have been taught to my Ph.D. students again and again. I hope this book
saves me from that repetitive efforts.


The source of the book is at
<https://github.com/statds/stat-writing>.


The notes are prepared with the **bookdown** R package [@xie2016bookdown], which
can be installed from CRAN or Github: 

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is
defined by the first-level heading `#`.


To compile this example to PDF, you need XeLaTeX. You are recommended to install
TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
